Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-07 lqg-strings.tex
Added wedge in flat-space Polyakov action and made d's non-curly (sorry I have this habit of differential d being straight)
Did same as before to curved-space Polyakov action
Made omega's in the text have  internal2 indices to match eq(7)

\begin{equation}\label{eqn:polyakov-flat}
	S_{P} = -\frac{T}{2} \int d\tau d\sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation}
Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.

@@

\begin{equation}\label{eqn:polyakov-gravity}
	S'_{P} = -\frac{T}{2} \int d\tau d\sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
\end{equation}

@@

Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$. Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega_a^i$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu I}$. However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega_a^i$, we can replace $X^{\mu I}$ with $X^{\mu i}$.
\begin{equation}\label{eqn:lqg-string-action}
	S_{PA} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma\,e\,e^a_i\,e^b_j \, D_a X^{\mu i} D_b X^{\nu j} E_\mu^I E_{\nu I},
\end{equation}
where $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
\begin{equation}\label{eqn:worldsheet-deriv}
	D_a X^{\mu i} = \partial_a X^{\mu i} + \omega_{a\,j}^i X^{\mu j},
\end{equation}
where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.

>>>>

\begin{equation}\label{eqn:polyakov-flat}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation}
Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.

@@

\begin{equation}\label{eqn:polyakov-gravity}
	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
\end{equation}

@@

Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$. Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu I}$. However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu I}$ with $X^{\mu i}$.
\begin{equation}\label{eqn:lqg-string-action}
	S_{PA} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma\,e\,e^a_i\,e^b_j \, D_a X^{\mu i} D_b X^{\nu j} E_\mu^I E_{\nu I},
\end{equation}
where $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
\begin{equation}\label{eqn:worldsheet-deriv}
	D_a X^{\mu i} = \partial_a X^{\mu i} + \omega_{a\,j}^i X^{\mu j},
\end{equation}
where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.
